Muhammad Suhail
Bangalore

H + (91) 9895 370025
B suhail.ars@gmail.com
Í github.com/suhailars
Blog: http: // suhailars. blogspot. in

Summary
{ Enthusiastic developer with 3 years of professional hands-on experience creating cutting-edge web
applications seeking challenging employment
{ Having more than 1 year of experience in Game Development using JavaScript(Game Closure)
{ Extensively worked on developing web application using Python and JavaScript

Technical Skill
Key Skill
Platforms
Databases
Web
Game
Technologies

Python, JavaScript, C++, Racket
Linux, Windows
PostgreSQL, MongoDB, MySQL
Django, Flask, Falcon, AngularJs, Node.js
Game Closure
Facebook Games, Celery, AWS, Elasticsearch, Redis

Education
2008–2012 B.Tech, Govt. Engineering College, Palakkad, 60%.
2006–2008 HSE, GMHSS, Thenhipalam, 80%.
2006 SSLC, CRHSS, Velimukku, 85%.

Experience
{ Web Developer
- Pytech, Mumbai, India
- Role: Web application Developer
- Duration: From 2014 April to 2014 September 20
- Link: http://www.pytech.in/
{ Web Developer
- Zerodha, Banglore, India
- Role: Web application Developer
- From 2014 Sept 20 to 2015 Feb 20
- Link: https://zerodha.com/
{ Full Stack Developer
- Hashcube, Banglore, India
- Role: Full Stack Developer
- From 2015 April to 2016 Sept
- Link: http://hashcube.com/

{ Full Stack Developer
- Fortraiz, Banglore, India
- Role: Full Stack Developer
- From 2016 Nov to Present
- Link: http://www.fortraiz.com/

Projects Worked On
{ Ecom
Ecomexpress is a ecommerce website used to manage the various stages of a product delivery
The site handles around a million shipments per month. The project covers all stages from the
initial pickup of product from a customer until delivering the product to consignees.
Languages/Tools: Python, Django, JavaScript
{ Index
Index is a logistic service. The site handles thousands of shipments daily. The project covers
all stages from the initial pickup of product from a customer until delivering the product to
consignees.
Languages/Tools: Python, Django, JavaScript
{ Q
Q is next generation back office tool for trading. It is a financial digital assistant for investors.
Languages/Tools: Flask, jQuery/JavaScript, SQLAlchamy
Link: https://q.zerodha.com/
{ Sudoku Quest
Sudoku Quest is a classical quest based game having more than 1 million users and 600 various
levels. The game is completley developed using open-source engine GameClosure
Languages/Tools: GameClosure, JavaScript, Node.js
Link: Play Store
{ Gummy Pop
Gummy Pop is a casual quest based game having more than 2 lakhs users and 300 various levels.
The game is completley developed using open-source engine GameClosure
Languages/Tools: GameClosure, JavaScript, Node.js
Link: Play Store
{ SMTA
Social Media Threat Analysis (SMTA) is the process of monitoring socia media and detected
threats to any organization using artificial intelligence
Languages/Tools: Python, Falcon, AngularJs, ElasticSearch


