\documentclass[11pt,a4paper]{moderncv}

% moderncv theme
\moderncvtheme[blue]{classic}

% character encoding
\usepackage[utf8]{inputenc}

% page margin
\usepackage[scale=0.8]{geometry}
\usepackage{textcomp}

% personal data
\firstname{Muhammad}
\familyname{Suhail}
\mobile{+91 9895 37 00 25}
\email{suhail.ars@gmail.com}
\homepage{https://github.com/suhailars}
\extrainfo{{Blog:} {\small{\url{http://suhailars.blogspot.in/}}}}
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Technical skills}
    \cvcomputer{Languages}
           {Python, Javascript, Shell Scripting}
           {\textbf{Version Control}: }
           {Git}

    \cvcomputer{Databases}
           {MySQL, PostgreSQL, MongoDB}
           {\textbf{Frameworks}: }
           {Django, Flask, Falcon, GameClosure, AngularJs, Node.js}

    \cvcomputer{Tools: }
           {Celery, AWS, Elasticsearch, Redis, Memcached}
           {\textbf{Platforms}: }
           {GNU/Linux (Arch linux, Debian, Ubuntu \& Fedora)}

\section{Education}
    \cventry{2008 -- 2012}{B.Tech}{Govt. Engineering College}{}{}{Palakkad, Kerala, India}

\section{Work Experience}
    \begin{itemize}
        \item Software Engineer
        \begin{itemize}
            \item Zerodha, Bangalore, India
            \item Role: Web application Developer
            \item link: {\url{https://zerodha.com/}}
            \item Duration: From 2014 April to 2015 March 
        \end{itemize}
    \end{itemize}
    \begin{itemize}
        \item Software Engineer
        \begin{itemize}
            \item Hashcube, Bangalore, India
            \item Role: Full Stack Developer  
            \item {\url{http://hashcube.com/}}
            \item Duration: From 2015 April to 2016 Sept
        \end{itemize}
    \end{itemize}
    \begin{itemize}
        \item Senior Software Engineer
        \begin{itemize}
            \item Thoughtchimp, Bangalore, India
            \item Role: Backend Developer
            \item {\url{http://www.thoughtchimp.com/}}
            \item Duration: From 2016 Nov to 2017 Sept
        \end{itemize}
    \end{itemize}
 
\pagebreak
\section{Projects Worked on}
    \cvline{Title}{\textbf{Q}}
    \cvline{}{\small Q is next generation back office tool for trading. It is a financial digital assistant for investors.}
    \cvline{Languages/Tools:}{Flask, jQuery/JavaScript, SQLAlchamy}

    \cvline{Title}{\textbf{AppRank.in}}
    \cvline{}{\small A website which tracks Google Play app rankings.}
    \cvline{Website}{\small{\url{https://apprank.in}}}

    \cvline{Title}{\textbf{SMS Attendance}}
    \cvline{}{\small Daily attendance SMS alert for MES College of Engineering students. During the period when project was active, it had more than 2300 registered users (out of 2700 students).}
    \cvline{Source}{\small{\url{https://j15h.nu/source/attendance}}}

    \cvline{Title}{\textbf{Unicalbot}}
    \cvline{}{\small A bot that checks for notifications and exam results from University of Calicut website and tweets about it.}
    \cvline{Source}{\small{\url{https://j15h.nu/source/unical}}}

    \cvline{Title}{\textbf{Yet Another 2048}}
    \cvline{}{\small Popular web based puzzle game 2048, re-written and optimized for mobile.}
    \cvline{Website}{\small{\url{https://j15h.nu/2048}}}
    \cvline{Source}{\small{\url{https://j15h.nu/source/2048}}}

    \cvline{Title}{\textbf{DeskWiki Editor}}
    \cvline{}{\small A desktop client to edit MediaWiki websites.}
    \cvline{Source code}{\small{\url{https://j15h.nu/source/wiki}}}

    \cvline{Title}{\textbf{Blender Add-Ons}}
    \cvline{}{\small Developed a set of blender add-ons for architects.}
    \cvline{Source code}{\small{\url{https://j15h.nu/source/wall},\newline \url{https://j15h.nu/source/library}}}

    \cvline{Title}{\textbf{Publish Your Bookmarks}}
    \cvline{}{\small Simple tool to publish Firefox bookmarks as a webpage.}
    \cvline{Source code}{\small{\url{https://j15h.nu/source/bookmark}}}

\pagebreak

\section{Free/Libre/OpenSource Software Contributions}
    \cvline{Silpa}{\small{\url{http://silpa.org.in}}}
    \cvline{jquery.i18n}{\small{\url{https://github.com/wikimedia/jquery.i18n}}}
    \cvline{jquery.ime}{\small{\url{https://github.com/wikimedia/jquery.ime}}}
    \cvline{Game Closure}{\small{\url{https://github.com/gameclosure/devkit}}}
    \cvline{CyanogenMod}{\small{\url{http://www.cyanogenmod.org/}}}
    \cvline{GNOME Localization}{\small{\url{http://l10n.gnome.org}}}
    \cvline{SMC Fonts}{\small{\url{https://github.com/smc/fonts}}}
    \cvline{Devkit Helper}{\small{\url{https://github.com/hashcube/DevkitHelper}}}
    \cvline{Debian diaspora progressbar}{\small{\url{https://gitorious.org/debian-diaspora/progressbar}}}
    \cvline{Askbot}{\small{\url{http://askbot.org}}}

\section{Activities \& Achievements}
    \cvline{*}{\textbf{Google Summer of Code} (GSOC) Mentor - 2013, 2014 and 2016. }
    \cvline{*}{\textbf{SMS Attendance} and \textbf{Indic Keyboard} featured on national dailies, Deccan Chronicle, The Hindu, Times of India, Indian Express, The Economic Times, Malayala Manorama, Deshabhimani and Mathrubhumi.}
    \cvline{*}{\textbf{Indic Keyboard} ranked \#1 in India, Saudi Arabia and UAE on top new free tools list.}
    \cvline{*}{DeskWiki was one of the 100+ selected applications in the \textbf{Ubuntu App Showdown} contest.}
    \cvline{*}{Yourstory.com wrote a profile on their techie tuesdays column - \small{\url{https://yourstory.com/2017/03/techie-tuesdays-jishnu-mohan/}}}

\section{Blogs \& Social Media}
    \cvline{Github}{\url{http://github.com/jishnu7}}
    \cvline{Behance}{\url{https://www.behance.net/jishnu7}}
    \cvline{Medium}{\url{https://medium.com/@jishnu7}}
    \cvline{Personal/tech}{\url{http://blog.j15h.nu}}
    \cvline{Android blog}{\url{http://androidtweak.in}}

\end{document}
